Scalar Feedback based Joint Time-Frequency Precoder interpolation for MIMO-OFDM Systems

### 2019-12-09 paper/main.tex
adding cost207 plots
Add minor fixes

Fig.~\ref{fig:error_decay}, shows the rate at which error diminishes
with time for the proposed approach and direct quantization on the
Stiefel manifold using codebooks described
in~\cite{Gupt1905:Predictive}. We see that, since the adaptation of
independent scalar parameters causes the error to decay rapidly, the
error is lower and the convergence is faster.
\begin{figure}
\includegraphics[width=0.5\textwidth]{images/stief_veh.pdf}
\caption{\label{fig:error_decay}A comparison of the $4\times 2$ precoder quantization error vs. time instant for
  the proposed approach (labelled ``TODO'') and direct quantization on
the Stiefel manifold for the Vehicular channel profile.}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{images/cost0035}
\caption{BER vs. SNR for QPSK transmission over the $4\times 2$ 1024
  subcarrier MIMO-OFDM system, with the ITU Cost207-RA channel profile
  for $f_dT_s = 3.5\times 10^{-6}$, corresponding to a velocity of 36 km/h.}
\label{fig:ber_ped}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{images/cost01}
\caption{BER vs. SNR for QPSK transmission over the $4\times 2$ 64
  subcarrier MIMO-OFDM system, with the ITU Cost207-RA channel profile
  for $f_dT_s = 1.05\times 10^{-5}$, corresponding to a velocity of 108 km/h.}
\label{fig:ber_veh}
\end{figure}

>>>>

Fig.~\ref{fig:error_decay}, shows the rate at which error diminishes
with time for the proposed approach and direct quantization on the
Stiefel manifold using codebooks described
in~\cite{Gupt1905:Predictive}. We see that, since the adaptation of
independent scalar parameters causes the error to decay rapidly, the
error is lower and the convergence is faster, even though the starting
error is higher in the case of the scalar quantization approach.
\begin{figure}
\includegraphics[width=0.5\textwidth]{images/qerror.pdf}
\caption{\label{fig:error_decay}A comparison of the $4\times 2$
  precoder quantization error vs. time instant for the proposed
  approach (labelled ``Cost207\_RA Scalar'') and direct quantization
  on the Stiefel manifold (labelled ``Cost207\_RA Manifold'') for the COST207 channel profile.}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{images/cost1024_0035}
\caption{BER vs. SNR for QPSK transmission over the $4\times 2$ 1024
  subcarrier MIMO-OFDM system, with the ITU Cost207-RA channel profile
  for $f_dT_s = 3.5\times 10^{-6}$, corresponding to a velocity of 36 km/h.}
\label{fig:ber_ped}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{images/cost64_001}
\caption{BER vs. SNR for QPSK transmission over the $4\times 2$ 64
  subcarrier MIMO-OFDM system, with the ITU Cost207-RA channel profile
  for $f_dT_s = 1.05\times 10^{-5}$, corresponding to a velocity of 108 km/h.}
\label{fig:ber_veh}
\end{figure}
